---
title: "Perceived Challenges in Climate Action Implementation: How Demographics and Income Influence Barriers to Policy Uptake"
subtitle: "Lower-Income and Minority Groups Face Greater Perceived Obstacles to Climate Solutions"
author: 
  - Lexi Knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/climate_challenges_toronto](https://github.com/LexiKnight/climate_challenges_toronto)."
date: today
date-format: long
abstract: "Understanding public perceptions of climate action challenges is crucial for effective policy design and community engagement. This study analyzes survey responses from diverse demographic groups to identify which climate actions—across buildings, energy, transportation, consumption, and greenspace—are perceived as the most difficult to implement. We found that lower-income individuals and racial minority groups reported greater barriers, particularly in adopting energy-efficient technologies and sustainable transportation. These findings highlight the need for equitable and targeted policy support to ensure that climate initiatives are accessible and feasible for all members of society."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

# Introduction

Overview paragraph
Estimand paragraph
Results paragraph
Why it matters paragraph

The remainder of this paper is structured as follows: @sec-data presents the methods used to analyze these demographic differences, followed by @sec-results, which details the results of the comparison between Rosedale-Moore Park and Downtown Yonge East. @sec-discussion offers a discussion of the findings, highlighting the implications for understanding residential segregation in Toronto. Finally, @sec-conclusion concludes with a reflection on the limitations of the study and suggestions for future research directions.






# Data {#sec-data}
## Software and R-packages
## Methodology 
### Data Collection
### Data Cleaning
### Data Analysis
## Features
### 


# Model {#sec-model}

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model Specifications ###
### Model Justification 
We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.
#### Response Variable ####
#### Input Variabless ####
#### Model Structure ####
#### Parameter Estimation ####

# Results
Our results are summarized in @tbl-modelresults.


# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Limitations

## Future Directions

# Conclusion {#sec-conclusion}


\newpage

\appendix

# Appendix {#sec-appendix}

\newpage

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```


\newpage


# References


